Evaluating Variable Importances

### 2019-06-06 Scripts/evaluating_variable_importances.Rmd
edits from tuning mtry

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub("_dist", "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

@@

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(all_varimps_gm12878$ave10kb, decreasing = TRUE),]
#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

@@

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(all_varimps_K562$ave10kb, decreasing = TRUE),]
#all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

>>>>

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_tfbs.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

@@

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_chromstates.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
#GM12878
all_varimps_gm12878 <- cbind.data.frame(varimp_gm12878_10kb$Feature,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878 <- all_varimps_gm12878[order(rowMeans(all_varimps_gm12878[,-1]), decreasing = TRUE),]
#all_varimps_gm12878 <- all_varimps_gm12878[1:20,]
all_varimps_gm12878 <- melt(all_varimps_gm12878)

@@

#K562
all_varimps_K562 <- cbind.data.frame(varimp_K562_10kb$Feature,
                                        varimp_K562_10kb$aveimp10kb,
                                        varimp_K562_25kb$aveimp25kb,
                                        varimp_K562_50kb$aveimp50kb,
                                        varimp_K562_100kb$aveimp100kb)
names(all_varimps_K562) <- c("Feature", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_K562 <- all_varimps_K562[order(rowMeans(all_varimps_K562[,-1]), decreasing = TRUE),]
#all_varimps_K562 <- all_varimps_K562[1:20,]
all_varimps_K562 <- melt(all_varimps_K562)

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)		
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "Gm12878-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
                              chrs[i],
									            "/smote/distance/enet/rfimpvars_histones.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                                   "K562-",
	                                   "_dist",
	                                   "-Haib", 
                                     "-Sydh",
                                     "-Uta",
                                     "-Uw",
                                     "-Broad",
                                     "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]
